Paper 1 Analysis

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Additional info on PT delta_1 case.

<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP. The ``x'' indicates location of base model value.">>=
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}

@@

ggplot(mapping = aes_string(x = "delta_1_plot")) +
  stat_density(data = Rho_1_PT_data %>% filter(method != "orig"), geom = "line") +
  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
  geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
  xlab(expression("1 - "*delta[1])) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)

>>>>

<<PT-resample-meta, echo = TRUE, include = TRUE>>=
mod <- models$PT$adjusted$withE$CES$kle
# mod
print(mod$coefficients[["delta_1"]], digits = 20)
1 - mod$coefficients[["delta_1"]]

# Look at SSE of the actual model and the boundary model.
# First, the actual model:
sum(resid(mod)^2)
# Now, the boundary model with delta_1 = 1, namely boundary model 11.
mod11 <- attr(mod, "model.attempts")[[11]]
# mod11
sum(resid(mod11)^2)
@

<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
PTresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
any(PTresample$delta_1 >= 1)
1 - max(PTresample$delta_1)
range95 <- quantile(PTresample$delta_1, probs=c(0.025, 0.975))
range95
1 - range95
@

<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap="Bootstrap resampling density distribution of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP. The $\\times$ indicates location of base model value. Vertical lines show the range of the middle 95\\% of the distribution.">>=
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}

@@

ggplot(mapping = aes_string(x = "delta_1_plot")) +
  stat_density(data = Rho_1_PT_data %>% filter(method != "orig"), geom = "line") +
  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
  geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
  geom_vline(aes(xintercept = 1-range95), colour="gray50", size=0.1) +
  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
  xlab(expression("1 - "*delta[1])) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
